Global adjoint tomography -- Model GLAD-M25

### 2018-10-12 main.tex
highlight Jeroen's edit section

\section{Introduction}
With the development of high performance computing and numerical methods, it is now possible to using adjoint method to image the interior the globe using thousands of earthquakes.

@@

@@

\section{Earthquakes}
In addition to the 256 earthquakes used in the first generation model GLAD-M15, we
carefully picked 784 more earthquakes from Global Centroid-Moment-Tensor catalog\citep{}
and added them into our database, making the total number of earthquakes reach 1,040.
The lower band of moment magnitude, is set at 5.5 to ensure the signal-to-noise ratio at
the global scale. The upper bound of magnitude is set at 7.2 and duration of earthquakes
is set at 9 sec since we can use point representation and Gaussian-type source
time function.
We also constrain the duration of CMT sources to be smaller than 17s.
The locations of 1040 earthquakes is shown in fig.\ref{fig:source_correction}a.

@@

\subsection{Forward simulation}
The forward simulation takes the CMT sources, stations and Earth models as input.
We will first generate mesh based on the models. The CMT sources and station will
be fed into the solver to generate synthetic seismograms and forward wavefield snapshots.
SEPCFEM3D\_GLOBE with GPU acceleration is used on Titan at the Oak Ridge Nation Lab for
both mesher and solver part.

@@

\subsection{Adjoint Simulation}
The adjoint simulation takes the adjoint sources as input, and calculate the frechet
derivatives as output. The computation cost is about twice as the forward simulation since
it is both calculating the adjoint wavefiled and reconstruct the forward wavefield.
Other than the adjoint sources, the adjoint simulation also reads in the saved forward
wave, to fully incorporate attenuation and more exactly calculate the anelastic
sensitivity kernels.
After the adjoint simulation is done, the save wavefield could be deleted and disk
space would be freed.
One Adjoint simulation takes about 25 mins for 17sec resolution for 120min simulation
at 17s resolution.

@@

\subsection{Global Velocity Structure}
In Fig.\ref{fig:global-vs}, the global map of isotropic $V_s$ is plotted at certain depths.
As comparisons, we also plotted two other models, S362ANI+M{\citep{moulik2014anisotropic},
which is the updated version of our starting model but with mode data added
into the inversion, and S40RTS\citep{ritsema2011s40rts}. At the first glance,
you may notice that all the models agree at the long wavelength structures.
At 2800km depth, our model is very close to S362ANI+M, with more extended
features at the LLSVP.

@@

\subsubsection{North America}
The deployment of USArray has dramatically increased the data overage on the
continental United States. In this section, we compare our GLAD-M25 with
together with two global models, S362ANI+M, S40RTS, and two regional models,
US22\citep{zhu2017radial}, SL2013NA\citep{schaeffer2014imaging}.

>>>>

\section{Introduction}

{\color{Red} Wenjie: I want to leave this part to the end, when I finished reading all the papers.}

With the development of high performance computing and numerical methods, it is now possible to using adjoint method to image the interior the globe using thousands of earthquakes.

@@

{\color{Red} Wenjie: Read for Jeroen to edit}

@@

\section{Earthquakes}

{\color{Red} Wenjie: Read for Jeroen to edit}

In addition to the 256 earthquakes used in the first generation model GLAD-M15, we
carefully picked 784 more earthquakes from Global Centroid-Moment-Tensor catalog\citep{}
and added them into our database, making the total number of earthquakes reach 1,040.
The lower band of moment magnitude, is set at 5.5 to ensure the signal-to-noise ratio at
the global scale. The upper bound of magnitude is set at 7.2 and duration of earthquakes
is set at 9 sec since we can use point representation and Gaussian-type source
time function.
We also constrain the duration of CMT sources to be smaller than 17s.
The locations of 1040 earthquakes is shown in fig.\ref{fig:source_correction}a.

@@

\subsection{Forward simulation}

{\color{Red} Wenjie: Read for Jeroen to edit}

The forward simulation takes the CMT sources, stations and Earth models as input.
We will first generate mesh based on the models. The CMT sources and station will
be fed into the solver to generate synthetic seismograms and forward wavefield snapshots.
SEPCFEM3D\_GLOBE with GPU acceleration is used on Titan at the Oak Ridge Nation Lab for
both mesher and solver part.

@@

\subsection{Adjoint Simulation}

{\color{Red} Wenjie: Read for Jeroen to edit}

The adjoint simulation takes the adjoint sources as input, and calculate the frechet
derivatives as output. The computation cost is about twice as the forward simulation since
it is both calculating the adjoint wavefiled and reconstruct the forward wavefield.
Other than the adjoint sources, the adjoint simulation also reads in the saved forward
wave, to fully incorporate attenuation and more exactly calculate the anelastic
sensitivity kernels.
After the adjoint simulation is done, the save wavefield could be deleted and disk
space would be freed.
One Adjoint simulation takes about 25 mins for 17sec resolution for 120min simulation
at 17s resolution.

@@

\subsection{Global Velocity Structure}

{\color{Red} Wenjie: Plan to work more on this part. But do you any suggestion what things should I talk about?}

In Fig.\ref{fig:global-vs}, the global map of isotropic $V_s$ is plotted at certain depths.
As comparisons, we also plotted two other models, S362ANI+M{\citep{moulik2014anisotropic},
which is the updated version of our starting model but with mode data added
into the inversion, and S40RTS\citep{ritsema2011s40rts}. At the first glance,
you may notice that all the models agree at the long wavelength structures.
At 2800km depth, our model is very close to S362ANI+M, with more extended
features at the LLSVP.

@@

\subsubsection{North America}

{\color{Red} Wenjie: Read for Jeroen to edit}

The deployment of USArray has dramatically increased the data overage on the
continental United States. In this section, we compare our GLAD-M25 with
together with two global models, S362ANI+M, S40RTS, and two regional models,
US22\citep{zhu2017radial}, SL2013NA\citep{schaeffer2014imaging}.
